\documentclass[a4paper]{article}

\usepackage[utf8x]{inputenc}    
\usepackage[T1]{fontenc}
\usepackage{pgffor}


\usepackage[box,completemulti]{automultiplechoice}    


\newcounter{ocrfieldcount}[AMCquestionaff]
\newcommand{\ocrfield}[1]{
  \AMCboxDimensions{shape=square,height=2em,width=1.5em,down=.5em,rule=.5pt}
  \foreach \n in {1,...,#1}{%
    \hspace{-\fboxrule}%
    \csname AMC@answerBox@\endcsname{}{}{1}{case:\csname AMCid@name\endcsname:\the\csname AMCid@quest\endcsname,\theocrfieldcount}\stepcounter{ocrfieldcount}%
  }
}


\begin{document}



\onecopy{10}{    

%%% beginning of the test sheet header:    

\noindent{\bf QCM  \hfill TEST}

\vspace*{.5cm}
\begin{minipage}{.4\linewidth}
\centering\large\bf Test\\ Examination on Jan., 1st, 2008\end{minipage}
\namefield{\fbox{    
                \begin{minipage}{.5\linewidth}
                  Firstname and lastname:

                  \vspace*{.5cm}\dotfill
                  \vspace*{1mm}
                \end{minipage}
         }}

\begin{center}\em
Duration : 10 minutes.

  No documents allowed. The use of electronic calculators is forbidden.


  Questions using the sign \multiSymbole{} may have
  zero, one or several correct answers.  Other questions have a single correct answer.

  Negative points may be attributed to \emph{very
    bad} answers.
\end{center}
\vspace{1ex}

%%% end of the header

\begin{question}{prez}    
  Among the following persons, which one has ever been a President of the French Republic?
  \begin{choices}
    \correctchoice{René Coty}
    \wrongchoice{Alain Prost}
    \wrongchoice{Marcel Proust}
    \wrongchoice{Claude Monet}
  \end{choices}
\end{question}


\begin{questionmult}{OCR}    
  Among the following persons, which one has ever been a President of the French Republic?

  \ocrfield{3} and   \ocrfield{3} 
\end{questionmult}


\begin{questionmult}{OCR2}    
  Among the following persons, which one has ever been a President of the French Republic?

  \ocrfield{7} and   \ocrfield{2} 
\end{questionmult}



\begin{questionmult}{pref}    
  Among the following cities, which ones are French prefectures?
  \begin{choices}
    \correctchoice{Poitiers}
    \wrongchoice{Sainte-Menehould}
    \correctchoice{Avignon}
  \end{choices}
\end{questionmult}

% \AMCaddpagesto{3} 

}   

\end{document}
